Does pre-crastination explain why some observers are sub-optimal in a visual search task?

### 2023-09-28 RegReport/paper.tex
fixing tenses up to hyopotheses

% \maketitle
\begin{abstract}
How do we decide where to search for a target? Optimal search relies on first considering the relative informational value of different locations, and then executing eye movements to the best options. But many participants consistently move their eyes to locations that can be easily ascertained to neither contain the target, nor to provide new information about the target's location. Here we \textcolor{red}{asked} whether this sub-optimal search behaviour represents a specific example of a general tendency towards \textit{pre-crastination}: starting sub-goals of a task before they are needed, and in so doing, spending longer doing the task than is necessary. To test this hypothesis, we \textcolor{red}{asked} 200 participants to do two tasks: retrieve two heavy buckets (one close and one far), and search for a line segment. Pre-crastination is defined as consistently picking up the closer bucket first, versus the more efficient strategy of picking up the farther bucket first. Search efficiency is the proportion of fixations directed to more cluttered regions of the search array. We \textcolor{red}{predicted} an association of pre-crastination with inefficient search strategies. Personality inventories will also be administered to identify stable characteristics associated with these strategies. \textcolor{red}{We found no evidence of an association between search strategy, pre-crastination, or any of the personality measures collected.}
\end{abstract}

@@

In the present study, we investigate the hypothesis that participants who are sub-optimal in our split-half line segment search task have a tendency towards \textit{pre-crastination}, a phenomenon where participants prioritise the completion of a sub-goal, even if it results in extra effort overall \cite{rosenbaum2014}. In the original study, participants were asked to walk down a corridor, pick up one of two heavy buckets as they passed, and carry it to the finish line. The two buckets were placed at different distances between the start and finish line, and the optimal (in terms of minimising effort) strategy is to pick up the bucket that is furthest from the starting position and closer to the finish line. Despite this simple solution, most participants favoured picking up the first bucket they came to, even though that resulted in them having to carry it further. This tendency was named \textit{pre-crastination}, and has since been replicated several times in both humans \cite{fournier2019task} and pigeons \cite{wasserman2015}. In an even more dramatic version of the task, Fournier and colleagues (2019) asked participants to go get two buckets - one close and one further away - and bring them back to set them on a table behind them. The majority (36 out of 49 participants in the key condition) chose to pick up the close bucket first, carry it out to the further bucket, and then bring both back, even though this order is clearly more effortful than picking up the far bucket and then grabbing the close one on the way back to the table.

As a first step to assessing our hypothesis, we conducted a pilot study to ensure we would replicate the variability between participants in a shorter version of the search task, and that we could clearly classify people into two groups based on whether they pick up the close bucket first (i.e. "pre-crastinators") or the farther bucket (optimal). The pilot data were also intended to be used to refine our approach to data processing, visualization, and analysis. Both of the previous findings (search variability, \cite{nowakowska2017}, and pre-crastination, \cite{fournier2019task}) were clearly replicated in the pilot experiment. Surprisingly, the data suggested a relatively robust relationship between pre-crastination and visual search strategy, but in the opposite direction to the one which we originally expected, with pre-crastinators having a tendency to search more efficiently rather than less. We therefore revised our aim to be more data-driven than the original hypothesis, aiming to estimate the variability in search performance accounted for by pre-crastination. The pilot data also suggested that the relationship between pre-crastination and visual search may by mediated by differences in speed-accuracy trade-offs between participants, so we plan to explore this aspect of visual search as well.

If we confirm the existence of a relationship between these two tasks, a natural question is whether this can be accounted for by personality traits of the individuals.  A personality trait is an enduring pattern of thoughts, feelings, and behaviours that is stable across time and contexts \cite{funder2016}. Previous research suggests that those who precrastinate are motivated, responsible, and energetic \cite{rosenbaum2019}. Specifically, \cite{sauerberger2019} found a correlation of $r = 0.22$ between precrastinaion and  conscientiousness, which we will attempt to replicate. Speculatively, these traits may also cause participants to search in a more thorough, but less efficient, manner, aligning with the interpretation that precrastinating, although costly, may not be irrational to the degree that participants prefer maximizing thoroughness over maximizing efficiency. Examining personality traits in this study will help to further uncover the individual difference factors associated with precrastination and different visual search strategies.

Our experiment tests the hypothesis that pre-crastination might represent a rational approach to doing tasks, i.e., a reasonable tendency to get the difficult part of the task out of the way first. If precrastination is positively related to efficient search, this would be evidence in favour of a ``rational'' interpretation of precrastination, as opposed to the alternative interpretation that it reflects an irrational impulse to grab the closest task-related object (in which case, a negative correlation with search efficiency would be more likely). In addition, the experiment has the potential to assess whether the already-established link between pre-crastination and conscientiousness could generalize, and be a potential explanation for the wide range of different search strategies previously observed. This would have important implications for theories of visual search, which tend to make assumptions about how ''people'' (as a group) direct their eyes during search; if personality traits can be directly predictive of eye movement strategies, this will challenge the field to more carefully refine its assumptions. In addition to the clear theoretical contribution our results could have, they could also illustrate that efficient/optimal tendencies in one circumstance can translate to inefficient choices in others. Finally, we have noticed in many fields that there is a lack of correlational studies relating behavioural measures to each other (as opposed to relating behavioural measures to personality traits).

@@

As such, we will investigate the following hypotheses:

>>>>

% \maketitle
\begin{abstract}
How do we decide where to search for a target? Optimal search relies on first considering the relative informational value of different locations, and then executing eye movements to the best options. But many participants consistently move their eyes to locations that can be easily ascertained to neither contain the target, nor to provide new information about the target's location. Here we \textcolor{red}{asked} whether this sub-optimal search behaviour represents a specific example of a general tendency towards \textit{pre-crastination}: starting sub-goals of a task before they are needed, and in so doing, spending longer doing the task than is necessary. To test this hypothesis, we \textcolor{red}{asked} 200 participants to do two tasks: retrieve two heavy buckets (one close and one far), and search for a line segment. Pre-crastination is defined as consistently picking up the closer bucket first, versus the more efficient strategy of picking up the farther bucket first. Search efficiency is the proportion of fixations directed to more cluttered regions of the search array. \textcolor{red}{Based on pilot data, we predicted} an association of pre-crastination with inefficient search strategies. Personality inventories \textcolor{red}{were} also administered to identify stable characteristics associated with these strategies. \textcolor{red}{In the final dataset, there was no clear association between search strategy and pre-crastination, nor did these correlate strongly with any of the personality measures collected.}
\end{abstract}

@@

In the present study, we \textcolor{red}{investigated} the hypothesis that participants who are sub-optimal in our split-half line segment search task have a tendency towards \textit{pre-crastination}, a phenomenon where participants prioritise the completion of a sub-goal, even if it results in extra effort overall \cite{rosenbaum2014}. In the original study, participants were asked to walk down a corridor, pick up one of two heavy buckets as they passed, and carry it to the finish line. The two buckets were placed at different distances between the start and finish line, and the optimal (in terms of minimising effort) strategy is to pick up the bucket that is furthest from the starting position and closer to the finish line. Despite this simple solution, most participants favoured picking up the first bucket they came to, even though that resulted in them having to carry it further. This tendency was named \textit{pre-crastination}, and has since been replicated several times in both humans \cite{fournier2019task} and pigeons \cite{wasserman2015}. In an even more dramatic version of the task, Fournier and colleagues (2019) asked participants to go get two buckets - one close and one further away - and bring them back to set them on a table behind them. The majority (36 out of 49 participants in the key condition) chose to pick up the close bucket first, carry it out to the further bucket, and then bring both back, even though this order is clearly more effortful than picking up the far bucket and then grabbing the close one on the way back to the table.

As a first step to assessing our hypothesis, we conducted a pilot study to ensure we would replicate the variability between participants in a shorter version of the search task, and that we could clearly classify people into two groups based on whether they pick up the close bucket first (i.e. "pre-crastinators") or the farther bucket (optimal). The pilot data were also intended to be used to refine our approach to data processing, visualization, and analysis. Both of the previous findings (search variability, \cite{nowakowska2017}, and pre-crastination, \cite{fournier2019task}) were clearly replicated in the pilot experiment. Surprisingly, the data suggested a relatively robust relationship between pre-crastination and visual search strategy, but in the opposite direction to the one which we originally expected, with pre-crastinators having a tendency to search more efficiently rather than less. We therefore revised our aim to be more data-driven than the original hypothesis, aiming to estimate the variability in search performance accounted for by pre-crastination. The pilot data also suggested that the relationship between pre-crastination and visual search may by mediated by differences in speed-accuracy trade-offs between participants, so we \textcolor{red}{planned} to explore this aspect of visual search as well.

If we confirm the existence of a relationship between these two tasks, a natural question is whether this can be accounted for by personality traits of the individuals.  A personality trait is an enduring pattern of thoughts, feelings, and behaviours that is stable across time and contexts \cite{funder2016}. Previous research suggests that those who precrastinate are motivated, responsible, and energetic \cite{rosenbaum2019}. Specifically, \cite{sauerberger2019} found a correlation of $r = 0.22$ between precrastinaion and conscientiousness, which we \textcolor{red}{attempted} to replicate. Speculatively, these traits may also cause participants to search in a more thorough, but less efficient, manner, aligning with the interpretation that precrastinating, although costly, may not be irrational to the degree that participants prefer maximizing thoroughness over maximizing efficiency. Personality traits in this study \textcolor{red}{were examined} to help further uncover the individual difference factors associated with precrastination and different visual search strategies.

Our experiment \textcolor{red}{tested} the hypothesis that pre-crastination might represent a rational approach to doing tasks, i.e., a reasonable tendency to get the difficult part of the task out of the way first. If precrastination \textcolor{red}{had been} positively related to efficient search, this would be evidence in favour of a ``rational'' interpretation of precrastination, as opposed to the alternative interpretation that it reflects an irrational impulse to grab the closest task-related object (in which case, a negative correlation with search efficiency would \textcolor{red}{have been} more likely). In addition, the experiment \textcolor{red}{had} the potential to assess whether the already-established link between pre-crastination and conscientiousness could generalize, and be a potential explanation for the wide range of different search strategies previously observed. This would have important implications for theories of visual search, which tend to make assumptions about how ''people'' (as a group) direct their eyes during search; if personality traits can be directly predictive of eye movement strategies, this \textcolor{red}{would} challenge the field to more carefully refine its assumptions. In addition to the clear theoretical contribution our results could have \textcolor{red}{had}, they could also \textcolor{red}{have illustrated a case where} efficient/optimal tendencies in one circumstance can translate to inefficient choices in others. Finally, we have noticed in many fields that there is a lack of correlational studies relating behavioural measures to each other (as opposed to relating behavioural measures to personality traits).

@@

As such, we \textcolor{red}{investigated} the following hypotheses:
